\pdfbookmark[0]{Abstract}{abstract}
\chapter*{Abstract}
\hypertarget{abstract}{}

Project Zoom is a software tool developed for the HPI School of Design Thinking (D-School) to support the documentation of innovative projects. While working on Design Thinking projects, the students' teams generate a lot of documents, such as presentations, photos, videos and text documents. The proposed tool allows them to visualize their creative process in an interactive graph. This enables not only the team members but also teachers and staff members to gain important insights into the projects. The information is stored persistently and can be accessed even months after the project was completed. Furthermore, the tool provides an overview of all projects at the D-School which makes it easier to share insights across projects and to acquire new ones.

This Bachelor Thesis covers the client application of Project Zoom. First, the use cases and requirements of the system, which were established as a result of the design process, are introduced. Project Zoom is designed to use a web-based client-server architecture. This enables multi-platform support and access from any internet-connected computer. The client application utilizes an event-driven architecture and implements the concept of Operational Transformation to provide a real-time collaboration experience. As the application applies the Model-View-Controller (MVC) pattern, this thesis also describes the concepts of the Model, View and Controller components in detail. Finally, some implementation considerations are explained and the system is evaluted based on the previously established use cases and requirements.